Centralized Programming for Distributed Control Planes

### 2016-01-27 paper/introduction.tex
intro edits

In the remainder of the paper, we review BGP~\ref{sec:background} (readers
familiar with BGP may skip this section),
further motivate the need for new languages 
for programming distributed control planes (Section \ref{sec:motivation}),
introduce \sysname{} by example (Section \ref{sec:propane}), 
explain our compiler algorithms (Section \ref{sec:compilation}),
present several lemmas justifying the correctness of our techniques (Section \ref{sec:theory}), describe our implementation (Section \ref{sec:implementation}
and discuss related work (Section \ref{sec:related}).

>>>>

\dpw{The following could be cut for space.}
In the remainder of the paper, we review BGP (Section~\ref{sec:background}---readers
familiar with BGP may skip this section),
further motivate the need for new languages 
for programming distributed control planes (Section \ref{sec:motivation}),
introduce \sysname{} by example (Section \ref{sec:propane}), 
explain our compiler algorithms (Section \ref{sec:compilation}),
present several lemmas justifying the correctness of our techniques (Section \ref{sec:theory}), describe our implementation (Section \ref{sec:implementation})
evaluate our work  (Section \ref{sec:evaluation}) and discuss related work (Section \ref{sec:related}).
